\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\title{Internet-X: An Identity-First Overlay Transport with Authenticated Locator Rebinding and Explicit Crypto Agility}
\author{mussolene}
\date{April 19, 2026}

\begin{document}
\maketitle

\begin{abstract}
Internet-X is an identity-first overlay architecture organized around the explicit chain Name $\rightarrow$ Identity $\rightarrow$ Locator $\rightarrow$ Path. The contribution is not the invention of identifier/locator separation or mobility support in isolation, both of which have substantial prior art, but a coherent protocol composition that combines stable cryptographic identity, explicit flow establishment, authenticated locator rebinding, packet-inspectable control semantics, a minimally real authenticated control-plane service, and explicit crypto-agility hooks for post-quantum transition. This paper presents the current Internet-X MVP reference profile, describes its runnable implementation, positions it against related work, and states clear limitations. The repository supports a real classical secure baseline with simulated post-quantum transition logic, not a claim of current post-quantum security or production readiness.
\end{abstract}

\section{Problem Statement}
Contemporary Internet transports and overlays often overload a small number of tokens with multiple semantic roles: application naming, endpoint identity, current network attachment, and routing behavior. This complicates mobility and makes it easy to conflate stable communication context with transient locator state. Internet-X addresses this by keeping four layers explicit: Name, Identity, Locator, and Path.

\section{Related Work}
The closest architectural relative is the Host Identity Protocol (HIP) \cite{rfc9063,rfc7401,rfc8046}. LISP \cite{rfc9299,rfc9300} and ILNP \cite{rfc6740} provide strong prior art for identifier/locator separation and overlay coexistence. QUIC \cite{rfc9000,rfc9001} provides important evidence that modern transports can bind control parameters into a transcript and survive address change without losing the connection abstraction. IKEv2 and MOBIKE \cite{rfc7296,rfc4555} demonstrate mature secure rebinding procedures. WireGuard \cite{wireguard} shows that a compact roaming-capable secure tunnel can be both readable and robust. Hybrid post-quantum transition work in TLS \cite{hybridtls} narrows the novelty of hybrid composition itself.

The repository therefore positions Internet-X as a compositional architecture and transition package rather than an entirely new primitive.

\section{Architecture}
Internet-X resolves communication through:
\begin{enumerate}[leftmargin=*]
\item Name: a human-meaningful handle.
\item Identity: a stable cryptographic node identity represented by a \texttt{NodeID}.
\item Locator: mutable current reachability information.
\item Path: the selected route or forwarding policy relative to the locator.
\end{enumerate}

In the current reference profile, \texttt{NodeID} is derived as \texttt{SHA-256(algorithm\_id || signing\_public\_key\_b64)}. That keeps the identity stable across locator changes while allowing the locator to change as network attachment changes.

\section{Protocol Design}
The reference handshake uses the required five phases: \texttt{INIT}, \texttt{INIT\_ACK}, \texttt{KEM\_EXCHANGE}, \texttt{AUTH}, and \texttt{DATA}. The responder then returns \texttt{DATA\_ACK}. After establishment, a peer may send \texttt{LOCATOR\_UPDATE} to authenticate a new locator for the same flow.

The JSON packet envelope keeps control semantics visible for debugging and research. The common envelope includes version, packet type, session identifier, flow identifier, sequence number, source and destination identities, locator hint, and a packet-specific payload.

\section{Cryptographic Profile}
The current implementation uses a real classical secure baseline: Ed25519 signatures, X25519 ephemeral key exchange, HKDF-SHA256 key derivation, and ChaCha20-Poly1305 for application data. The implementation advertises an explicit simulated hybrid PQ mode that mixes simulated shares into the session derivation context. This is a transition hook only; it is not real ML-KEM or ML-DSA security.

\section{Handshake And Locator Rebinding}
The key design choice is that flow establishment is explicit and identity-bound. A flow exists only after the responder issues \texttt{AUTH} with a transcript-bound \texttt{FlowID}. Locator change is not accepted as a naked network event. It is carried in a signed and MACed \texttt{LOCATOR\_UPDATE} packet and acknowledged explicitly by the peer.

\section{Threat Model}
The repository addresses off-path spoofing, transcript tampering, downgrade attempts, replayed data packets, malformed packet injection, and locator hijack attempts against an established flow. It does not claim resistance to endpoint compromise, malicious directory infrastructure, side-channel leakage, or global traffic analysis.

\section{Evaluation}
The repository evaluation is intentionally modest. It includes automated tests, an end-to-end demo, a bounded machine-checkable invariant model, and local loopback latency measurements. These artifacts are sufficient to argue that the reference design is coherent and runnable, but not sufficient to claim deployment readiness or universal superiority over production transports.

\section{Limitations}
The current package has significant limitations: the control plane is a single-instance, locally trusted authenticated service rather than a federated deployment substrate; path selection is not implemented as a standalone routing substrate; the PQ mode is simulated; the packet format is intentionally verbose; and the measurements are local rather than Internet-scale.

\section{Conclusion}
Internet-X is best understood as a strong design point under explicit constraints rather than as a universal replacement architecture. Its value lies in making identity-first communication, authenticated locator rebinding, and crypto-agile transition semantics concrete in one repository that another engineer can inspect, run, and critique.

\bibliographystyle{plain}
\bibliography{references}
\end{document}
